\documentclass[12pt]{article}
\usepackage{enumitem}
\begin{document}

\section*{Temperament Test Questionnaire}

Answer the following questions by selecting the option that best describes you.

\begin{enumerate}[label=\textbf{Q\arabic*.}]

\item In a group project, you usually…
\begin{enumerate}[label=(\Alph*)]
\item Share ideas and keep the group lively
\item Take charge and delegate tasks
\item Focus on details and ensure accuracy
\item Keep the peace and help where needed
\end{enumerate}

\item When meeting new people, you…
\begin{enumerate}[label=(\Alph*)]
\item Quickly make friends and chat easily
\item Introduce yourself confidently and lead conversations
\item Stay reserved and observe before speaking
\item Smile warmly and wait for others to approach
\end{enumerate}

\item If you face a big challenge, you…
\begin{enumerate}[label=(\Alph*)]
\item Stay optimistic and encourage others
\item Tackle it head-on with determination
\item Plan carefully and analyze solutions
\item Stay calm and take things step by step
\end{enumerate}

\item Your friends describe you as…
\begin{enumerate}[label=(\Alph*)]
\item Fun and outgoing
\item Confident and ambitious
\item Thoughtful and organized
\item Kind and dependable
\end{enumerate}

\item When making decisions, you prefer…
\begin{enumerate}[label=(\Alph*)]
\item Going with what feels exciting
\item Acting quickly and decisively
\item Thinking deeply and weighing pros/cons
\item Avoiding conflict and choosing harmony
\end{enumerate}

\item In a classroom, you’re most likely to…
\begin{enumerate}[label=(\Alph*)]
\item Answer questions eagerly
\item Lead group discussions
\item Take detailed notes
\item Support classmates quietly
\end{enumerate}

\item Your energy comes from…
\begin{enumerate}[label=(\Alph*)]
\item Being around people and socializing
\item Working toward goals and challenges
\item Learning and reflecting quietly
\item Relaxed environments and routines
\end{enumerate}

\item When a conflict arises, you…
\begin{enumerate}[label=(\Alph*)]
\item Try to lighten the mood with humor
\item Assert your viewpoint strongly
\item Think carefully before responding
\item Avoid arguments and keep the peace
\end{enumerate}

\item How do you handle stress?
\begin{enumerate}[label=(\Alph*)]
\item Distract myself with fun activities
\item Push harder to solve the problem
\item Worry and overthink details
\item Stay calm and take things slowly
\end{enumerate}

\item Your biggest strength is…
\begin{enumerate}[label=(\Alph*)]
\item Friendliness and enthusiasm
\item Confidence and leadership
\item Precision and thoughtfulness
\item Patience and reliability
\end{enumerate}

\item In a team, you prefer to…
\begin{enumerate}[label=(\Alph*)]
\item Motivate and inspire others
\item Direct and make decisions
\item Organize and structure tasks
\item Support and keep harmony
\end{enumerate}

\item When faced with new technology, you…
\begin{enumerate}[label=(\Alph*)]
\item Try it out immediately
\item Learn quickly and take charge
\item Read instructions carefully
\item Wait to see how others use it
\end{enumerate}

\item If you had a free weekend, you’d…
\begin{enumerate}[label=(\Alph*)]
\item Go out with friends
\item Work on a project or goal
\item Stay in and read or research
\item Relax at home with family
\end{enumerate}

\item People often come to you for…
\begin{enumerate}[label=(\Alph*)]
\item Fun and laughter
\item Decisions and guidance
\item Advice and careful analysis
\item Comfort and support
\end{enumerate}

\item When solving a puzzle, you…
\begin{enumerate}[label=(\Alph*)]
\item Guess and experiment
\item Try to solve it quickly
\item Work carefully step by step
\item Stay patient until it’s done
\end{enumerate}

\item In arguments, you are…
\begin{enumerate}[label=(\Alph*)]
\item Talkative and persuasive
\item Strong and firm
\item Cautious and precise
\item Quiet and accommodating
\end{enumerate}

\item When others make mistakes, you…
\begin{enumerate}[label=(\Alph*)]
\item Forgive quickly and move on
\item Get frustrated and correct them
\item Criticize carefully for improvement
\item Stay calm and help them
\end{enumerate}

\item Your study/work style is…
\begin{enumerate}[label=(\Alph*)]
\item Energetic but sometimes scattered
\item Fast and result-oriented
\item Careful and perfectionist
\item Consistent and steady
\end{enumerate}

\item When giving a speech, you…
\begin{enumerate}[label=(\Alph*)]
\item Enjoy entertaining the audience
\item Speak confidently and with authority
\item Worry about mistakes but prepare well
\item Prefer short, calm remarks
\end{enumerate}

\item Your weakness might be…
\begin{enumerate}[label=(\Alph*)]
\item Getting distracted easily
\item Being too controlling
\item Overthinking or worrying
\item Being too passive
\end{enumerate}

\item You like work that is…
\begin{enumerate}[label=(\Alph*)]
\item Social and engaging
\item Competitive and challenging
\item Structured and detailed
\item Relaxed and predictable
\end{enumerate}

\item If your plans change suddenly, you…
\begin{enumerate}[label=(\Alph*)]
\item Adapt quickly and laugh it off
\item Take control and make new plans
\item Feel uncomfortable and stressed
\item Stay calm and adjust slowly
\end{enumerate}

\item Your communication style is…
\begin{enumerate}[label=(\Alph*)]
\item Expressive and lively
\item Direct and commanding
\item Careful and precise
\item Gentle and calm
\end{enumerate}

\item You are most motivated by…
\begin{enumerate}[label=(\Alph*)]
\item Fun and excitement
\item Achievements and success
\item Accuracy and knowledge
\item Stability and peace
\end{enumerate}

\item In group activities, you…
\begin{enumerate}[label=(\Alph*)]
\item Entertain everyone
\item Lead the team
\item Organize and analyze
\item Support quietly
\end{enumerate}

\item When learning something new, you…
\begin{enumerate}[label=(\Alph*)]
\item Jump in with curiosity
\item Compete to master it quickly
\item Study carefully and in detail
\item Learn steadily over time
\end{enumerate}

\item Your friends would say you…
\begin{enumerate}[label=(\Alph*)]
\item Bring fun to the group
\item Push them to succeed
\item Give deep, thoughtful advice
\item Are always there for them
\end{enumerate}

\item You dislike…
\begin{enumerate}[label=(\Alph*)]
\item Being bored or ignored
\item Losing control or being weak
\item Chaos or lack of structure
\item Conflict or pressure
\end{enumerate}

\item If you’re given a hard assignment, you…
\begin{enumerate}[label=(\Alph*)]
\item Try to make it fun
\item Attack it head-on with determination
\item Break it into detailed steps
\item Work calmly until it’s done
\end{enumerate}

\item Your dream environment is…
\begin{enumerate}[label=(\Alph*)]
\item Exciting, social, and lively
\item Competitive and goal-driven
\item Organized, quiet, and structured
\item Peaceful, friendly, and balanced
\end{enumerate}

\end{enumerate}

\end{document}
